---
title: "Data Tidying and Filtering"
author: "Edwin Rivas Meraz"
date: "5/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load required packages
```{r}

load.packages <- function(x){if(class(x) != 'character') 
  stop("Error: packages listed in vector are not characters!") #includes a sanity check 
  lapply(x, require, character.only = TRUE)
}

packs <- c('readxl', 'tidyverse', 'dplyr', 'kableExtra')
load.packages(packs)
```


## Reading in the data
```{r}
Master <- read_csv(file = "DOEMSIPP_Incubations_Data.csv")
```

## Table it
```{r}

kable(Master) %>%
  kable_styling(bootstrap_options = c("striped", "hover", 'condensed'))

```

### How are the variables organized? What does each row represent? Each column?

## Filter Filter Filter
```{r}
ORP <- Master %>% filter(projectcode == 'DOE2', analyte == 'ORP')

#designate the columns that should have numeric values
cols.num <- names(ORP[,8])
  
#converts all desingated columns to numeric
ORP[cols.num] <- lapply(ORP[cols.num],as.numeric)

#Take the mean of rows grouped by incubation day and treament (i.e. Mn 3d)
ORP.mean <- ORP %>%
  group_by(incubationdays, treatment) %>%
  summarise_at(vars(measvalue), funs(mean(., na.rm=TRUE))) # remove na values


ORP.mean %>% ggplot(aes(x = incubationdays, y = measvalue, color = treatment)) + geom_point() + facet_wrap(~treatment) + geom_path() + ggtitle('ORP') + theme_classic()

```

### What does each component of the ggplot do?

### How would you improve this figure?

### Choose another analyte and make a similar figure. If you think another type of figure would better display this data let me know and I can help you build it.
